Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks

### 2025-03-20 Phase_II/draft/intro.tex
edit by Prof. Sarangi

\textcolor{magenta}{With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations. Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks. In astronomical image reconstruction projects, a common challenge is that the ground-truth data are often noisy, incomplete, or both. Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it. Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.}

\textcolor{magenta}{Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation. Generative Adversarial Networks (GANs), introduced by Ian Goodfellow et al. \citep{goodfellow2014generative}, have been successful in data augmentation tasks. Conditional GAN (cGAN) architectures, proposed by Mirza \& Osindero \citep{mirza2014conditional} and applied to a wide variety of datasets by Isola et al. \citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.}

\textcolor{magenta}{In the astrophysical context, Schawinski et al. \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images. Mustafa et al. \citep{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures. Coccomini et al. \citep{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies. They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe. 
}

>>>>

With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations. Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks. In astronomical image reconstruction projects, a common challenge is that the ground-truth data are often noisy, incomplete, or both. Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it. Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.

Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation. Generative Adversarial Networks (GANs), introduced by Ian Goodfellow et al. \citep{goodfellow2014generative}, have been successful in data augmentation tasks. Conditional GAN (cGAN) architectures, proposed by Mirza \& Osindero \citep{mirza2014conditional} and applied to a wide variety of datasets by Isola et al. \citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.

In the astrophysical context, Schawinski et al. \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images. Mustafa et al. \citep{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures. Coccomini et al. \citep{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies. They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe.

### 2025-03-20 Phase_II/draft/main.tex
edit by Prof. Sarangi

\begin{abstract}
In current astronomy, the simulation of Intensity Interferometry is demonstrating significant advancements in the high-precision resolution of stellar objects at optical wavelengths. Despite these achievements, phase retrieval remains challenging due to photon correlation. This paper proposes the application of a conditional Generative Adversarial Network (GAN) to address this issue of image reconstruction with Intensity Interferometry. Here, the GAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star. This innovative approach promises to enhance the capabilities of Intensity Interferometry for image reconstruction in addition to estimating the parameters with high precision in astronomical observations.
\end{abstract}
\input{intro}
\input{II}
\input{GAN}
\input{ParaGan}
\input{Result}
\input{conclusion}

>>>>

\begin{abstract}
In modern astronomy, simulations of Intensity Interferometry are making significant strides in achieving high-precision resolution of stellar objects at optical wavelengths. Despite these advancements, phase retrieval remains a major challenge due to the nature of photon correlation. This paper explores the application of a conditional Generative Adversarial Network (GAN) to tackle the problem of image reconstruction in Intensity Interferometry. The proposed GAN-based approach effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by leveraging sparsely sampled, phase-subtracted Fourier transforms of the source. This method not only enhances the image reconstruction capabilities of Intensity Interferometry but also enables precise parameter estimation in astronomical observations.  
\end{abstract}
\input{intro}
\input{II}
\input{GAN}
\input{ParaGan}
\input{Result}
\input{conclusion}
